\chapter{Core Optics}
%\section{Core Optics}
\label{sec:Appendix_Core_optics}

\section{Candidate materials for low noise substrates}
At room temperature fused silica is the best material that can be used as substrate due to its very low thermoelastic effect and ultra low optical and mechanical losses.
At cryogenic temperatures crystalline materials have to replace fused silica. The main challenge is the production of homogeneous large volume substrates with low enough defects and optical absorption. In general, crystalline materials have much less Brownian noise at cryogenic temperatures due to their ordered lattice structure.
\subsection{Silica}
The homogeneity of the refractive index is the main issue here. For the substrates of the cavity mirrors, excellent homogeneity is only important in the two dimensions perpendicular to the beam axis. This can be achieved even for large volumes (corresponding to a total mass of several hundred kilograms). However, the beam splitter requires a very high homogeneity in all three dimensions and this can currently only be guaranteed by the manufacturers for masses up to 40 kg (diameter 55 cm, thickness 7 cm). The company Heraeus has planned some tests to push this limit to about 100 kg. Whether such large beam splitters are required depends on the optical layout of the detector and is under investigation.

\subsection{Silicon}
Silicon has a low mechanical loss at cryogenic temperatures (below 10 K is similar or lower than that of fused silica at room temperature), resulting in low substrate thermal noise. In addition, the thermal expansion coefficient of silicon is zero at $\sim$123\,K and 18\,K, leading to the ability to eliminate substrate thermoelastic noise and thermal expansion effects due to absorbed laser power.

Silicon is not transparent at the currently used wavelength of 1064\,nm. Initially, the telecommunications wavelength of 1550\,nm was proposed for use with silicon mirrors, due to wide availability of high-powered lasers and optical components. More recently, there has been growing interest in using a wavelength close to 2000\,nm. A major driver towards 2000\,nm is the development of amorphous silicon as a possible low thermal noise cryogenic coating material. Amorphous silicon exhibits significantly lower absorption (a factor of $\sim$7) at 2000\,nm than at 1550\,nm. It seems likely, therefore, that the choice of mirror coatings will be a major factor in the choice of wavelength for future detectors. 

Sufficiently low optical absorption can be obtained from silicon produced using the Float Zone technique. However, the maximum size of ingot which can be produced with this method is $\sim$200\,mm. This is too small for the requirements of future detectors (e.g. ET-LF requires 450\,mm diameter, 550\,mm thick optics). While larger diameter silicon pieces can be produced using the Czochralski method, the optical absorption of this type of silicon is too high, due to impurities related to the production method. A magnetic Czochralski process (MCz) exists, in which a magnetic field is used to reduce the impurity concentration in the centre of the ingot. This process can produce diameters of up to 450 mm, and a production line for manufacturing silicon of this diameter does exist at the company Shin Etsu, but is currently not operational. Initial studies of the optical absorption have shown low values at room temperature of $\sim$3\,ppm/cm at 1550\,nm and $\sim$5\,ppm/cm at 2000\,nm. The measurements showed and increase towards lower temperatures, reaching approximately 10\,ppm/cm at 50\,K. This is promising for meeting the requirement of 15\,ppm/cm for cryogenic silicon mirrors. However, initial studies indicate that the absorption of this material can vary significantly, both along the radius and along the length of an ingot, and more studies of the homogeneity of the absorption and its dependence on the thermal history of the sample are required. 

It will be important to test the optical scattering from MCz silicon, particularly as the MCz growth process is known to produce a high void content in the material. Work on this is underway at Glasgow and at Caltech. Initial scattering estimates at Glasgow \cite{SiliconScatter2017} suggest that the scattering is higher than in fused silica, but is likely to be within the required limits.

There is evidence that polishing silicon surfaces can increase their optical absorption. The presence of surface absorption was confirmed in a study in the IGR in Glasgow \cite{SiliconSurfaceAbsorpBell2017} and it was shown that a particular polishing process can be used which does not produce this effect. While this has been consistently demonstrated, further work is required to test whether a silicon surface can be polished to the specifications required for a GW detector without resulting in surface absorption.

Non-linear absorption in silicon is not expected to set a major limit to performance, contributing <\,0.5\,ppm/cm absorption for a wavelength of 2\,$\mu$m at the light intensity assumed for inside the LIGO Voyager ITM. At the significantly lower intensity within an ET-LF ITM, these effects are even less significant. Two-photon absorption generates free carriers in silicon: the absorption due to these free carriers depends crucially on the carrier life time. Experiments to measure this for magnetic Czochralski silicon are underway in a collaboration between Stanford and Glasgow.
\greencomment{Dave: I like including absorption mechanisms in this section.  But you don't talk about free carrier absorption, impurity absorption, etc... Presumably there are the main sources of absorption?  }

Two sources of phase noise in silicon optics have not yet been studied experimentally: thermo-refractive noise and carried density noise. These noise sources should be experimentally verified to ensure that they do not set unexpected limits of silicon mirror performance. An experiment targeted at measuring thermo-refractive noise in silicon is currently being constructed in Glasgow.

\subsection{Sapphire}
Sapphire is transparent at 1064\,nm and hence does not require a change from the currently used detector wavelength. Mechanical quality factors of sapphire samples are as high as few $10^8$ at room temperature\cite{Rowan_2000a} and they increase at cryogenic temperatures\cite{uchiyama1999mechanical}. 
% On mirror-size samples measurements are affected by the suspension systems used. 
Sapphire's elastic constants are about 3 times higher than silicon's, helping to reduce thermal noise. The thermal conductivity of sapphire increases with decreasing temperature and reaches a peak of several $10^3$\,W/(m \,K) around 20-40K.  Thermoelastic noise is also quite low due to the high thermal conductivity at low temperatures.  This high conductivity (and the low temperature coefficient) make the thermal lens effect negligible. The high Young's modulus of elasticity has two additional advantages: fewer parametric instabilities and a higher calibration frequency in a gravitational wave detector.
The optical absorption of sapphire has been found to vary strongly from crystal to crystal and for crystals from different suppliers. There is only a very small chance of finding sapphire crystals with low absorption by cherry-picking among a large number of products on the market. In KAGRA, it turned out that it was necessary to develop sapphire crystals with low absorption by working closely with the crystal manufacturers. Although it took some time, sapphire crystals were developed to meet 50ppm/cm with sufficient margin \cite{Hirose_2014a}. The production success rate due to the inclusion of bubbles is 1/8.
Theoretical work on scattering in sapphire sets a lower limit of 0.21\,ppm/cm, with higher measured values of around 13 ppm/cm being attributed to impurities and vacancies.
Sapphire's high Mohs hardness of 9 and its crystalline structure, resulting in orientation dependent machinability, makes it harder to process sapphire substrates. Polishing the KAGRA test masses took much longer than polishing the aLIGO test masses, although the size is smaller. Despite this hardness, no degradation in micro roughness or surface figure of the polished surfaces has been observed in KAGRA sapphire test masses\cite{Hirose_2014a}, compared to aLIGO or advanced VIRGO test masses made of fused silica. 
%More specifically, looking into Power Spectral Density (PSD) of uncoated surfaces at different spatial frequencies from $10^{-2}$ to $10^3$\,1/mm of both sapphire and fused silica,  no apparent degradation in sapphire has ever been observed.
Sapphire is known to be birefringent. Since sapphire is a uniaxial crystal, the alignment of the optical axis, called the c-axis, to the beam axis should theoretically make the refractive index uniform in the plane perpendicular to the beam axis. In reality, however, even with optimized alignment, it is common that the inhomogeneity of the refractive index of sapphire is one order of magnitude worse than that of fused silica. It is therefore essential to compensate for this by locally adjusting the thickness of the substrates. This can be achieved by aspherically polishing the back of the mirror, and the ion beam figuring technique (IBF) has been applied to the KAGRA ITMs.

Dielectric multilayer coating of SiO2 and Ta2O5 on sapphire substrates appear to be as good as such coatings deposited on silica substrates\cite{Hirose_2014b}.
The biggest c-axis sapphire window currently available in the market for gravitational wave detectors is about 220mm in diameter and 150mm in thickness (mass of 23 kg) although the ingot size is actually much larger. These are grown by either HEM or TSMG methods which assure the lowest dislocation density among all the production methods. If we allow crystals to have bubbles or apparent defects inside, the size could be much larger. The ingot size has been simply limited by size of furnace where sapphire crystal is grown.

The KAGRA monolithic suspensions (will) feature sapphire components for the core optic, the ears, fibers, and blade springs, attached using hydroxide catalysis and indium bonding~\cite{Kumar:2016_KAGRA}. KAGRA has demonstrated that sapphire can be successfully bonded through hydroxide catalysis bonding. Sapphire technology has also been extensively developed in order to produce mono--crystalline fibres of length greater than 1\,m and large plates of a large variety of thickness. \magentacomment{hal:what plates are those? for cutting fibres from them?}

A collaborative research project with a Japanese company got started targeting 100kg sapphire windows whose diameter is 400mm and thickness is 200mm. Developing that large size windows compatible with lower absorption and higher homogeneity will be a key to success toward 3G detectors with sapphire test mass mirrors
